\documentclass{resume}
\usepackage[left=0.5in,top=0.4in,right=0.5in,bottom=0.4in]{geometry}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{xcolor}
\hypersetup{
    colorlinks=true,
    urlcolor=blue
}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{SUFIYAN KHAN}
\address{Aspiring DevOps Engineer \textbar\ Cloud \& Infrastructure Automation Enthusiast}
\address{
\faPhone~+92 335 7543076 \quad
\faEnvelope~\href{mailto:sufikhan980@gmail.com}{sufikhan980@gmail.com} \quad
\faLinkedin~\href{https://linkedin.com/in/sufiyan-khan-cloud}{sufiyan-khan-cloud} \quad
\faGithub~\href{https://github.com/SufiyanKhanCloud}{SufiyanKhanCloud} \quad
\faGlobe~\href{https://sufiyan-khan-portfolio.lovable.app}{Portfolio}
}

\begin{document}
\begin{rSection}{Objective}
Aspiring DevOps Engineer with a solid foundation in cloud, CI/CD, Linux, Git, and containerization. Backed by hands-on projects and IBM-issued certifications in DevOps, Agile, and Shell scripting. Recently completed Google’s Prompting Essentials Specialization. Actively seeking a Junior DevOps role or internship to grow within a collaborative team.
\end{rSection}

\begin{rSection}{Skills}
\textbf{DevOps \& Tools:} Git, GitHub, GitLab, Jenkins, Docker, Docker Compose, CI/CD, Shell Scripting \\
\textbf{Cloud \& Infrastructure:} AWS EC2, Linux (Ubuntu), VirtualBox, VMware \\
\textbf{Languages \& Scripting:} Bash, YAML, Python (Beginner) \\
\textbf{Additional:} Prompt Engineering, Automation, Analytical Thinking
\end{rSection}


\begin{rSection}{Projects}

\item \textbf{Dockerized Expense Tracker} \\
Developed and deployed a Java Spring Boot + MySQL app using Docker Compose with persistent volumes on AWS EC2. Ensured zero downtime and reliable deployment. \\
\textit{\small Docker, Spring Boot, MySQL, AWS EC2, Linux} \hfill \faGithub~\href{https://github.com/SufiyanKhanCloud/docker-practice/tree/main/Expenses-Tracker-WebApp}{GitHub}

\item \textbf{Flask Microservice Architecture} \\
Built a two-tier Flask + MySQL application using Docker with volume mounts and networking. Deployed on EC2 within 10 minutes. \\
\textit{\small Flask, MySQL, Docker, AWS EC2, Linux} \hfill \faGithub~\href{https://github.com/SufiyanKhanCloud/docker-practice/tree/main/two-tier-flask-app}{GitHub}

\item \textbf{CI/CD Pipeline for Django App} \\
Built a Jenkins-based CI/CD pipeline using Groovy for a Django Notes App. Automated build, test, and deployment stages-cutting deployment time by 50\%. \\
\textit{\small Jenkins, Docker, Django, Groovy, GitHub, AWS EC2, Linux} \hfill \faGithub~\href{https://github.com/SufiyanKhanCloud/Django-Notes-App}{GitHub}

\end{rSection}

\begin{rSection}{Certifications}
\textbf{IBM: Introduction to DevOps} \hfill \href{https://www.coursera.org/account/accomplishments/verify/OIGBYO6L8GZJ}{\textit{Verify}} \\
\textbf{IBM: Introduction to Cloud Computing} \hfill \href{https://www.coursera.org/account/accomplishments/verify/O4EN4P7ZI6XV}{\textit{Verify}} \\
\textbf{IBM: Agile Development and Scrum} \hfill \href{https://www.coursera.org/account/accomplishments/verify/PV26WR8KH5MX}{\textit{Verify}} \\
\textbf{IBM: Linux and Shell Scripting} \hfill \href{https://www.coursera.org/account/accomplishments/verify/07JX8O7ZPDCY}{\textit{Verify}} \\
\textbf{IBM: Git and GitHub} \hfill \href{https://www.coursera.org/account/accomplishments/verify/6JZJJTDRFPBT}{\textit{Verify}} \\
\textbf{Google: Prompting Essentials Specialization} \hfill \href{https://www.coursera.org/account/accomplishments/specialization/Y6K56SVG21W2}{\textit{Verify}}
\end{rSection}

\begin{rSection}{Education}
\textbf{BS in Computer Science}, University of Karachi (UBIT) \hfill \textit{Feb 2023 -- Present} \\
\textbf{Intermediate (Pre-Engineering)}, DJ Sindh Govt. Science College \hfill \textit{Nov 2022} \\
\textbf{Matriculation (Science)}, Karachi Public School \hfill \textit{Oct 2020}
\end{rSection}

\begin{rSection}{DevOps Engagement \& Community Impact}
\item Created a viral LinkedIn post titled “Linux and Networking for DevOps,” earning 26K+ impressions, 135+ new followers, 67 reposts, and 75+ profile views.
\item Embrace “learning in public” by regularly sharing DevOps projects and insights through GitHub and LinkedIn.
\item Engage with DevOps communities to stay current on tools, workflows, and best practices.
\end{rSection}


\end{document}

