\documentclass{resume}
\usepackage[left=0.5in,top=0.4in,right=0.5in,bottom=0.4in]{geometry}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{xcolor}
\hypersetup{
    colorlinks=true,
    urlcolor=blue
}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Sufiyan Khan}
\address{Aspiring DevOps Engineer | Cloud & Infrastructure Automation Enthusiast}
\address{
\faPhone~+92 335 7543076 \quad
\faEnvelope~\href{mailto:sufiikhan980@gmail.com}{sufiikhan980@gmail.com} \quad
\faLinkedin~\href{https://linkedin.com/in/sufiyan-khan-cloud}{sufiyan-khan-cloud} \quad
\faGithub~\href{https://github.com/SufiyanKhanCloud}{SufiyanKhanCloud}
}

\begin{document}

%----------------------------------------------------------------------------------------
% OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{Objective}
Detail-oriented Computer Science student with hands-on experience in Docker, Linux, Git, Jenkins, and AWS. Completed IBM-certified DevOps courses on Coursera. Passionate about CI/CD pipelines, infrastructure automation, and deploying cloud-native applications on Linux systems. Seeking an entry-level DevOps role to contribute to efficient, scalable systems.
\end{rSection}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
\textbf{BS in Computer Science}, University of Karachi (UBIT) \hfill Feb 2023 -- Present \\
\textbf{Intermediate (Pre-Engineering)}, DJ Sindh Govt. Science College \hfill Nov 2022 \\
\textbf{Matriculation (Science)}, Karachi Public School \hfill Oct 2020
\end{rSection}

%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
\textbf{DevOps Tools:} Docker, Git, Jenkins, GitHub, GitLab, CI/CD, Shell Scripting \\
\textbf{Cloud/Infra:} AWS EC2, Linux (Ubuntu), VirtualBox, VMware \\
\textbf{Languages:} Bash, Python (basic) \\
\textbf{Soft Skills:} Critical Thinking, Self-Learning, Collaboration, Communication
\end{rSection}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}
\item \textbf{Dockerized Expense Tracker (Spring Boot)} — Containerized a Java web app with MySQL using Docker Compose; deployed on a Linux-based EC2 instance. Managed volumes and environment configs. \\
{\small \textit{Tools: Docker, Spring Boot, MySQL, AWS EC2, Linux, GitHub}} \\
\faGithub~\href{https://github.com/SufiyanKhanCloud/docker-practice/tree/main/Expenses-Tracker-WebApp}{View Repo}

\item \textbf{Flask + MySQL Microservice} — Built microservices using Flask and MySQL in isolated Docker containers. Deployed on EC2 Linux; ensured data persistence via Docker volumes. \\
{\small \textit{Tools: Flask, MySQL, Docker, AWS EC2, Linux, Git}} \\
\faGithub~\href{https://github.com/SufiyanKhanCloud/docker-practice/tree/main/two-tier-flask-app}{View Repo}

\item \textbf{CI/CD Pipeline for Django Notes App} — Automated build, test, and deployment via Jenkins. Built Docker image and deployed on Linux-based AWS EC2 using Groovy pipeline scripts. \\
{\small \textit{Tools: Jenkins, Docker, Django, GitHub, AWS EC2, Linux}} \\
\faGithub~\href{https://github.com/SufiyanKhanCloud/Django-Notes-App}{View Repo}
\end{rSection}

%----------------------------------------------------------------------------------------
% CERTIFICATIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{Certifications}
\textbf{IBM: Introduction to DevOps} \hfill \href{https://www.coursera.org/account/accomplishments/verify/OIGBYO6L8GZJ}{\textit{Verify}} \\
\textbf{IBM: Introduction to Cloud Computing} \hfill \href{https://www.coursera.org/account/accomplishments/verify/O4EN4P7ZI6XV}{\textit{Verify}} \\
\textbf{IBM: Introduction to Agile Development and Scrum} \hfill \href{https://www.coursera.org/account/accomplishments/verify/PV26WR8KH5MX}{\textit{Verify}} \\
\textbf{IBM: Introduction to Linux and Shell Scripting} \hfill \href{https://www.coursera.org/account/accomplishments/verify/07JX8O7ZPDCY}{\textit{Verify}} \\
\textbf{IBM: Getting Started with Git and GitHub} \hfill \href{https://www.coursera.org/account/accomplishments/verify/6JZJJTDRFPBT}{\textit{Verify}}
\end{rSection}

%----------------------------------------------------------------------------------------
% EXTRA-CURRICULAR
%----------------------------------------------------------------------------------------

\begin{rSection}{Extra-Curricular Activities}
\item Shared DevOps projects and technical content on LinkedIn to grow professional presence.
\item Published beginner-friendly tutorials on Docker, Git, and Linux basics.
\item Practiced Bash scripting and skeleton programming in Linux environments.
\item Engaged with open-source and DevOps communities for collaboration and learning.
\end{rSection}

\end{document}
