\documentclass{resume}
\usepackage[left=0.5in,top=0.4in,right=0.5in,bottom=0.4in]{geometry}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{xcolor}
\hypersetup{
    colorlinks=true,
    urlcolor=blue
}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{SUFIYAN KHAN}
\address{Aspiring DevOps Engineer, Cloud \& Infrastructure Automation Enthusiast}
\address{
\faPhone~+92 335 7543076 \quad
\faEnvelope~\href{mailto:sufikhan980@gmail.com}{sufikhan980@gmail.com} \quad
\faLinkedin~\href{https://linkedin.com/in/sufiyan-khan-cloud}{sufiyan-khan-cloud} \quad
\faGithub~\href{https://github.com/SufiyanKhanCloud}{SufiyanKhanCloud}
}

\begin{document}

\begin{rSection}{Objective}
Computer Science undergraduate with hands-on experience in Docker, Linux, Git, Jenkins, and AWS. Completed IBM DevOps certifications on Coursera. Passionate about building CI/CD pipelines, deploying containerized applications, and automating infrastructure on cloud environments. Open to internship or junior DevOps engineer roles to contribute and grow in real-world projects.
\end{rSection}

\begin{rSection}{Education}
\textbf{BS in Computer Science}, University of Karachi (UBIT) \hfill \textit{Feb 2023 -- Present} \\
\textbf{Intermediate (Pre-Engineering)}, DJ Sindh Govt. Science College \hfill \textit{Nov 2022} \\
\textbf{Matriculation (Science)}, Karachi Public School \hfill \textit{Oct 2020}
\end{rSection}

\begin{rSection}{Skills}
\textbf{DevOps Tools:} Docker, Git, Jenkins, GitHub, GitLab, CI/CD, Shell Scripting \\
\textbf{Cloud/Infra:} AWS EC2, Linux (Ubuntu), VirtualBox, VMware \\
\textbf{Languages:} Bash, Python (basic) \\
\textbf{Soft Skills:} Problem-Solving, Communication, Self-Learning, Team Collaboration
\end{rSection}

\begin{rSection}{Projects}

\item \textbf{Dockerized Expense Tracker} \\
Developed and deployed a Java Spring Boot + MySQL app using Docker Compose. Used persistent volumes and deployed on AWS EC2 with zero downtime. \\
\textit{\small Docker, Spring Boot, MySQL, AWS EC2, Linux} \hfill \faGithub~\href{https://github.com/SufiyanKhanCloud/docker-practice/tree/main/Expenses-Tracker-WebApp}{GitHub}

\item \textbf{Flask Microservice Architecture} \\
Built a two-tier Flask + MySQL setup using Docker containers with durable volumes. Deployed on EC2 in under 10 minutes. \\
\textit{\small Flask, MySQL, Docker, AWS EC2, Linux} \hfill \faGithub~\href{https://github.com/SufiyanKhanCloud/docker-practice/tree/main/two-tier-flask-app}{GitHub}

\item \textbf{CI/CD Pipeline for Django App} \\
Implemented Jenkins-based CI/CD pipeline with Groovy scripts for a Django Notes App. Reduced deployment time by 50\%. \\
\textit{\small Jenkins, Docker, Django, GitHub, AWS EC2, Linux} \hfill \faGithub~\href{https://github.com/SufiyanKhanCloud/Django-Notes-App}{GitHub}

\end{rSection}

\begin{rSection}{Certifications}
\textbf{IBM: Introduction to DevOps} \hfill \href{https://www.coursera.org/account/accomplishments/verify/OIGBYO6L8GZJ}{\textit{Verify}} \\
\textbf{IBM: Introduction to Cloud Computing} \hfill \href{https://www.coursera.org/account/accomplishments/verify/O4EN4P7ZI6XV}{\textit{Verify}} \\
\textbf{IBM: Agile Development and Scrum} \hfill \href{https://www.coursera.org/account/accomplishments/verify/PV26WR8KH5MX}{\textit{Verify}} \\
\textbf{IBM: Linux and Shell Scripting} \hfill \href{https://www.coursera.org/account/accomplishments/verify/07JX8O7ZPDCY}{\textit{Verify}} \\
\textbf{IBM: Git and GitHub} \hfill \href{https://www.coursera.org/account/accomplishments/verify/6JZJJTDRFPBT}{\textit{Verify}}
\end{rSection}

\begin{rSection}{Extra-Curricular Activities}

\item Created a viral LinkedIn post titled “Linux and Networking for DevOps” that gained over 26,000 impressions, 135+ followers, 159 reactions, 67 reposts, and 75 profile views.

\item Learning in public: Sharing GitHub projects and insights from personal DevOps learning journey through posts and open collaboration.

\item Actively engaged in DevOps communities to follow trends, tools, and best practices.

\end{rSection}

\end{document}
